|

### 2021-11-30 01-Chp-Background.Rmd
Back to clean, working version

All existing evidence, regardless of study design, is first identified by the by the systematic review presented inChapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading). Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise. [@Pagen71; @sterne2019; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.

>>>>

All existing evidence, regardless of study design, is first identified by the by the systematic review presented inChapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading). Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise. [@page2021; @sterne2019; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
